---
title: "group_06_package"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{group_06_package}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(group6.Rpackage)
```

# Description of package

This package includes functions for the central dogma including constructing a random DNA sequence, transcribing it into RNA, extracting codons, translating the codons into amino acids and finally plotting the amino acid composition.

# Function 1 - Line

# Function 2 - Sigrid

# Function 3 - Mathilde

### `extract_codons()`

The `extract_codons()` function splits a nucleotide sequence, which can be either DNA or RNA, into codons starting from a specified position. This is a key part of the translational process as these codons can then be translated into amino acids during the proteins synthesis.

#### **Usage**

```{r}
extract_codons(sequence, start = 1)
```

#### Arguments

-   sequence: A character string representing a nucleotide sequence composed of the letters A, T (or U), C, and G.

-   start: An integer specifying the position to begin reading codons. The default is 1 and if changed it will represent a different reading frame.

#### Value

Returns a character vector where each element corresponds to one codon (a triplet of nucleotides) extracted from the input sequence.

#### Details

The function calculates the total sequence length. It then uses substrig() to extract triplets of the seqeunce starting from the specified position. Only actual triplets will be returned and the remaining nucleotides at the end of the sequence will be ignored.

#### Examples

```{r}
# Example 1: Split a simple DNA sequence into codons
extract_codons("ATGCGATAA")
# Output: "ATG" "CGA" "TAA"

# Example 2: Start reading from the second position (frame shift)
extract_codons("ATGCGATAA", start = 2)
# Output: "TGC" "GAT"

# Example 3: RNA sequence example
extract_codons("AUGCGAUAA")
# Output: "AUG" "CGA" "UAA"
```

# Function 4 - Kristine

# Function 5 - Alberte

### `plot_aa_frequency()`

The `plot_aa_frequency()` function visualizes the composition of a protein or peptide sequence by plotting the frequency of each amino acid as a bar chart. This provides a quick overview of amino acid distribution, which can be useful for identifying compositional biases, comparing protein sequences, or validating sequence processing steps.

#### Usage

```{r}
plot_aa_frequency("sequence")
```

#### **Arguments**

-   **sequence** — A character string representing an amino acid sequence composed of single-letter amino acid codes (e.g., `"ACDEFGHIKLMNPQRSTVWY"`).

#### **Value**

A `ggplot2` bar plot showing the count of each amino acid in the provided sequence. Each bar corresponds to a unique amino acid, with height proportional to its frequency in the sequence.

#### **Details**

Internally, the function splits the input sequence into individual amino acids, counts their occurrences using `stringr::str_count()`, and constructs a frequency table. The result is rendered as a bar plot using `ggplot2` with a `theme_bw()` style. Amino acids are colored distinctly, but the legend is suppressed for visual clarity.

#### **Examples**

```{r}
# Example 1: Standard short amino acid sequence
plot_aa_frequency("ACDEFGHIKLMNPQRSTVWY")

# Example 2: Longer protein sequence (HLA-A*0101)
plot_aa_frequency("MAVMAPRTLLLLLSGALALTQTWAGSHSMRYFFTSVSRPGRGEPRFIAVGYVDDTQFVRFDSDAASQRMEPRAPWIEQEGPEYWDQETRNVKAQSQTDRVDLGTLRGYYNQSEAGSHTIQIMYGCDVGSDGRFLRGYRQDAYDGKDYIALNEDLRSWTAADMAAQITKRKWEAAHEAEQLRAYLDGTCVEWLRRYLENGKETLQRTDPPKTHMTHHPISDHEATLRCWALGFYPAEITLTWQRDGEDQTQDTELVETRPAGDGTFQKWAAVVVPSGEEQRYTCHVQHEGLPKPLTLRWELSSQPTIPIVGIIAGLVLLGAVITGAVVAAVMWRRKSSDRKGGSYTQAASSDSAQGSDVSLTACKV")

```

# Use cases and functions to include
