---
title: "group_06_package"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{group_06_package}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(group6.Rpackage)
```

# Description of package

This packange includes functions for the central dogma including constructing a random DNA sequence, transcribing it into RNA, extracting codons, translating the codons into amino acids and finally plotting the amino acid composition.

# Function 1 - Line

# Function 2 - Sigrid

# Function 3 - Mathilde

# Function 4 - Kristine

# Function 5 - Alberte

### `plot_aa_frequency()`

The `plot_aa_frequency()` function visualizes the composition of a protein or peptide sequence by plotting the frequency of each amino acid as a bar chart. This provides a quick overview of amino acid distribution, which can be useful for identifying compositional biases, comparing protein sequences, or validating sequence processing steps.

#### Usage

```{r}
plot_aa_frequency("sequence")
```

#### **Arguments**

-   **sequence** — A character string representing an amino acid sequence composed of single-letter amino acid codes (e.g., `"ACDEFGHIKLMNPQRSTVWY"`).

#### **Value**

A **ggplot2** bar plot showing the count of each amino acid in the provided sequence. Each bar corresponds to a unique amino acid, with height proportional to its frequency in the sequence.

#### **Details**

Internally, the function splits the input sequence into individual amino acids, counts their occurrences using `stringr::str_count()`, and constructs a frequency table. The result is rendered as a bar plot using **`ggplot2`** with a `theme_bw()` style. Amino acids are colored distinctly, but the legend is suppressed for visual clarity.

#### **Examples**

```{r}
# Example 1: Standard short amino acid sequence
plot_aa_frequency("ACDEFGHIKLMNPQRSTVWY")

# Example 2: Longer protein sequence (HLA-A*0101)
plot_aa_frequency("MAVMAPRTLLLLLSGALALTQTWAGSHSMRYFFTSVSRPGRGEPRFIAVGYVDDTQFVRFDSDAASQRMEPRAPWIEQEGPEYWDQETRNVKAQSQTDRVDLGTLRGYYNQSEAGSHTIQIMYGCDVGSDGRFLRGYRQDAYDGKDYIALNEDLRSWTAADMAAQITKRKWEAAHEAEQLRAYLDGTCVEWLRRYLENGKETLQRTDPPKTHMTHHPISDHEATLRCWALGFYPAEITLTWQRDGEDQTQDTELVETRPAGDGTFQKWAAVVVPSGEEQRYTCHVQHEGLPKPLTLRWELSSQPTIPIVGIIAGLVLLGAVITGAVVAAVMWRRKSSDRKGGSYTQAASSDSAQGSDVSLTACKV")

```

# Use cases and functions to include
